Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Pastry fixes
MorphMix fixes

	\subsection{Pastry} % 2001
		Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Pastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about log(n) steps.

@@

	\subsection{MorphMix} % 2002
		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

		MIX networks are typically high latency networks and traffic in it moves slow. Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order. Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead. MorphMix has been developed as a low latency and high performance network. As such, it will not hold messages for very long, nor will it use cover traffic.

>>>>

	\subsection{Pastry} % 2001
		Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Pastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about $\log(n)$ steps.

@@

	\subsection{MorphMix} % 2002
		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

		MIX networks are typically high latency and traffic in it moves slow. Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order. Often, cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead. MorphMix has been developed as a low latency and high performance network. As such, it will not hold messages for very long, nor will it use cover traffic.
